% Copyright 2013 Christophe-Marie Duquesne <chmd@chmd.fr>
% Copyright 2014 Mark Szepieniec <http://github.com/mszep>
% Copyright 2015 Eduardo Blancas <http://github.com/edublancas>
%
% Colors based on this paletter:
% http://www.colourlovers.com/palette/61082/Your_Best_Behaviour
% 
% ConText style for making a resume with pandoc. Inspired by moderncv.
% 
% This CSS document is delivered to you under the CC BY-SA 3.0 License.
% https://creativecommons.org/licenses/by-sa/3.0/deed.en_US

% Palettes
% https://designschool.canva.com/blog/website-color-schemes/
% http://www.onextrapixel.com/2013/10/25/40-stunning-website-designs-with-great-color-schemes/
% http://www.awwwards.com/trendy-web-color-palettes-and-material-design-color-schemes-tools.html

\startmode[*mkii]
  \enableregime[utf-8]  
  \setupcolors[state=start]
\stopmode

\setupcolor[hex]
\definecolor[namecolor][h=191919]
\definecolor[sectioncolor][h=333333]
\definecolor[linkcolor][h=4C4C4C]
%\definecolor[rulecolor][h=3B3738]

% Enable hyperlinks
\setupinteraction[state=start, color=linkcolor]

\setuppapersize [letter][letter]
\setuplayout    [width=middle, height=middle,
                 backspace=12mm, cutspace=0mm,
                 topspace=12mm, bottomspace=12mm,
                 header=0mm, footer=0mm]

%\setuppagenumbering[location={footer,center}]

% guide on styles http://wiki.contextgarden.net/Style_Alternatives#Font_Size
% \tfd, \tfb

% FONT SIZE AND STYLE
\setupbodyfont[9pt, helvetica]

% SPACING
% http://wiki.contextgarden.net/Command/setupwhitespace
\setupwhitespace[none]

\setupblackrules[width=31mm, color=rulecolor]

% fontsize \tf{a,b,c}
% http://tex.stackexchange.com/questions/294932/alternative-to-large-large-huge-small-etc-in-context

\setuphead[chapter]      [style=\tfd]

% NAME
\setuphead[section]      [style=\tfc\bf, color=namecolor, align=middle]

% SECTIONS
\setuphead[subsection]   [style=\tfb\bf, color=sectioncolor, align=middle,
                          ]%before={\leavevmode\blackrule\hspace}]

\setuphead[subsubsection][style=\bf]

\setuphead[chapter, section, subsection, subsubsection][number=no]

%\setupdescriptions[width=10mm]

\definedescription
  [description]
  [headstyle=bold, style=normal,
   location=hanging, width=18mm, distance=14mm, margin=0cm]

\setupitemize[autointro, packed]    % prevent orphan list intro
\setupitemize[indentnext=no]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setuptables[textwidth=max, HL=none]

\setupthinrules[width=15em] % width of horizontal rules

\setupdelimitedtext
  [blockquote]
  [before={\setupalign[middle]},
   indentnext=no,
  ]


\starttext

\section[eduardo-blancas-reyes]{Eduardo Blancas Reyes}

\placetable[none]{}
\starttable[|r|]
\HL
\NC \useURL[url1][mailto:e.blancas@columbia.edu][][e.blancas@columbia.edu]\from[url1]
/ \useURL[url2][https://blancas.io]\from[url2]
\NC\AR
\HL
\stoptable

\subsection[education]{Education}

{\bf Columbia University} \hfill  Aug 2017 - Dec 2018 (Expected)

M.S. in Data Science

Relevant coursework: Algorithms for Data Science, Machine Learning with
Probabilistic Programming.\crlf
\crlf
{\bf Universidad Nacional Autónoma de México (UNAM)} \hfill Aug 2016 -
Jun 2017

Graduate Certificate in Applied Statistics

Relevant coursework: Statistical Inference, Sampling Techniques,
Multivariate Analysis, Experimental Design, Categorical Data Analysis,
Regression Models and Bayesian Inference.\crlf
\crlf
{\bf Instituto Tecnológico y de Estudios Superiores de Monterrey
(ITESM)} \hfill Jan 2011 - May 2015

B.S. in Mechatronics Engineering. Graduated with honors.

Coursework in analog and digital electronics, instrumentation, control
theory, embedded systems.

\subsection[professional-experience]{Professional Experience}

{\bf Columbia University (Grossman Center for the Statistics of Mind)}
\hfill New York, NY

{\em Research Assistant (Advisor: Liam Paninski)} \hfill Sep 2017 -
Present

\startitemize[packed]
\item
  Apply novel Machine Learning tecniques to improve spike sorting
\item
  Develop an automated spike sorting library to analyze data from dense
  multielectrode arrays using Python, scikit-learn and Tensorflow
\stopitemize

{\bf Krieger} \hfill Mexico City, MX

{\em Lead Backend Engineer} \hfill Jun 2016 - Aug 2017

\startitemize[packed]
\item
  Oversaw backend development across projects to ensure code quality,
  performance and reliability
\item
  Developed internal software tools that are used in several ongoing
  projects (input validation, software versioning, deployment, user
  permissions). These tools have reduced development time and increased
  team's productivity
\item
  REST Web Services development using Python and Google Cloud\crlf
\stopitemize

{\bf University of Chicago (Center for Data Science and Public Policy)}
\hfill Chicago, IL

{\em Data Science Fellow (Advisor: Rayid Ghani)} \hfill May 2015 - Jun
2016

\startitemize[packed]
\item
  Developed a Machine Learning model using spatiotemporal data for the
  City of Cincinnati to identify properties at risk of building code
  violations. Engineering a fully automated and reproducible pipeline to
  ingest new datasets and update the model. Worked with more than 50GB
  of data.
\item
  Designed a predictive model for Infonavit (largest mortgage provider
  in Mexico) to predict home abandonment. Worked with more than 100GB of
  data
\stopitemize

\subsection[publications]{Publications}

\startitemize[packed]
\item
  K. Ackermann, {\bf E. Blancas Reyes}, S. He, T. Anderson Keller, P.
  van der Boor. R. Khan, R. Ghani. Designing Policy Recommendations to
  Reduce Home Abandonment in Mexico. In Proceedings of the 22nd ACM
  SIGKDD International Conference on Knowledge Discovery and Data
  Mining, KDD '16.
\item
  {\bf E. Blancas Reyes}, J. Helsby, K. Rasch, P. van der Boor, L.
  Haynes, R. Ghani, E. Cunningham. Early detection of properties at risk
  of blight using spatiotemporal data. Data for Policy 2016 at
  University of Cambridge.
\stopitemize

\subsection[skills]{Skills}

{\bf Programming languages}: Python, R, Objective-C, SQL. {\bf Tools and
technologies}: scikit-learn, numpy, flask, Google App Engine, Google
Cloud Datastore, Google Cloud Storage, PostgreSQL, PostGIS, Docker,
MongoDB, Amazon EC2, Amazon S3, Amazon Beanstalk

\stoptext
